---
title: "Draft"
format: html
execute: 
  echo: false
  warning: false
---

```{r}
library(tidyverse)

df <- readRDS("data/data_cleaned.rds")

compute_pct_by_country <- function(data, country, col) {
  data |>
    group_by({{country}}, {{col}}) |>
    count() |>
    group_by({{country}}) |>
    mutate(pct = 100 * n / sum(n))
}

plot_pct_by_country <- function(data, country, col, pct, n) {
  ggplot(data, aes(x = fct_rev({{col}}), y = {{pct}})) +
    geom_bar(stat = "identity") +
    geom_text(aes(label = paste0({{n}}, " (", round({{pct}}, 0), "%)")), hjust = -0.1, size = 3) +
    scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
    coord_flip() +
    facet_wrap(vars({{country}})) +
    labs(x = NULL, y = "Percentage") +
    theme_light()
}
```

## Gender

```{r}
#| fig-width: 8
#| fig-height: 4
#| out-width: "100%"
df_plot <- compute_pct_by_country(data = df, country = q2, col = q1)

plot_pct_by_country(data = df_plot, country = q2, col = q1, pct = pct, n = n)
```

## Years of experience

```{r}
#| fig-width: 8
#| fig-height: 4
#| out-width: "100%"
df_plot <- compute_pct_by_country(data = df, country = q2, col = q4)

plot_pct_by_country(data = df_plot, country = q2, col = q4, pct = pct, n = n)
```

## Organization

```{r}
#| fig-width: 8
#| fig-height: 4
#| out-width: "100%"
df_plot <- compute_pct_by_country(data = df, country = q2, col = q5_category)

plot_pct_by_country(data = df_plot, country = q2, col = q5_category, pct = pct, n = n)
```

## Job

```{r}
#| fig-width: 8
#| fig-height: 5.5
#| out-width: "100%"
df_plot <- compute_pct_by_country(data = df, country = q2, col = q7)

plot_pct_by_country(data = df_plot, country = q2, col = q7, pct = pct, n = n)
```

::: {.callout-note collapse="true" appearance="simple"}

## The "Others" that weren't be grouped

```{r}
df |> 
  filter(q7 == "Other, please specify:") |> 
  pull(q7_12_text)
```

:::

## Main questions by country

> I think research culture is evolving for the better

```{r}
#| fig-width: 8
#| fig-height: 4
#| out-width: "100%"
df_plot <- compute_pct_by_country(data = df, country = q2, col = q9_1)

plot_pct_by_country(data = df_plot, country = q2, col = q9_1, pct = pct, n = n)
```

> There is equity in decision-making and giving credit for research within my organisation

```{r}
#| fig-width: 8
#| fig-height: 4
#| out-width: "100%"
df_plot <- compute_pct_by_country(data = df, country = q2, col = q9_2)

plot_pct_by_country(data = df_plot, country = q2, col = q9_2, pct = pct, n = n)
```

> International research funders and/or foreign researchers dominate the research priorities of my country

```{r}
#| fig-width: 8
#| fig-height: 4
#| out-width: "100%"
df_plot <- compute_pct_by_country(data = df, country = q2, col = q9_3)

plot_pct_by_country(data = df_plot, country = q2, col = q9_3, pct = pct, n = n)
```

> I am satisfied with the way research performance is assessed my organization e.g., academic publications, or obtaining a research grant

```{r}
#| fig-width: 8
#| fig-height: 4
#| out-width: "100%"
df_plot <- compute_pct_by_country(data = df, country = q2, col = q9_4)

plot_pct_by_country(data = df_plot, country = q2, col = q9_4, pct = pct, n = n)
```

> At my organization, there is collaboration rather than competition between researchers

```{r}
#| fig-width: 8
#| fig-height: 4
#| out-width: "100%"
df_plot <- compute_pct_by_country(data = df, country = q2, col = q9_5)

plot_pct_by_country(data = df_plot, country = q2, col = q9_5, pct = pct, n = n)
```

> Do you think career progression (for instance, to senior positions) is harder for certain groups of researchers, e.g., women, early career researchers?

***Noted that this question may be incorrect for participants in Vietnamese, Lao PDR... due to an error in translation that I've reported to Nina***

```{r}
#| fig-width: 8
#| fig-height: 4
#| out-width: "100%"
df_plot <- compute_pct_by_country(data = df, country = q2, col = q10)

plot_pct_by_country(data = df_plot, country = q2, col = q10, pct = pct, n = n)
```

```{r}
#| fig-width: 10
#| fig-height: 6
#| out-width: "100%"
df_long <- df |> 
  # Step 1: Split comma-separated q11 into multiple rows
  separate_rows(q11, sep = ",") |> 
  # Step 2: Trim any extra whitespace
  mutate(q11 = str_trim(q11)) |> 
  drop_na(q11)

df_plot <- compute_pct_by_country(data = df_long, country = q2, col = q11)

plot_pct_by_country(data = df_plot, country = q2, col = q11, pct = pct, n = n)
```

::: {.callout-note collapse="true" appearance="simple"}

## The "Others" that weren't be grouped

```{r}
df |> 
  filter(q11_text_cleaned == "Others") |> 
  pull(q11_8_text)
```

:::

## Main questions by gender

Here I group "Non-binary/third gender", "Prefer not to say" and "Bayot" into "Others".

```{r}
#| fig-width: 3
#| fig-height: 1.5
df <- df |> 
  mutate(
    gender = q1,
    gender = if_else(gender %in% c("Non-binary / third gender", "Prefer not to say", "Bayot"), "Others", gender)
  )

df_plot <- df |> 
  group_by(gender) |>
  count() |> 
  mutate(pct = 100 * n / nrow(df))

ggplot(df_plot, aes(x = fct_rev(gender), y = pct)) +
    geom_bar(stat = "identity") +
    geom_text(aes(label = paste0(n, " (", round(pct, 0), "%)")), hjust = -0.1, size = 3) +
    scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
    coord_flip() +
    labs(x = NULL, y = "Percentage") +
    theme_light()
```

> I think research culture is evolving for the better

```{r}
#| fig-width: 8
#| fig-height: 4
#| out-width: "100%"
df_plot <- compute_pct_by_country(data = df, country = gender, col = q9_1)

plot_pct_by_country(data = df_plot, country = gender, col = q9_1, pct = pct, n = n)
```

> There is equity in decision-making and giving credit for research within my organisation

```{r}
#| fig-width: 8
#| fig-height: 4
#| out-width: "100%"
df_plot <- compute_pct_by_country(data = df, country = gender, col = q9_2)

plot_pct_by_country(data = df_plot, country = gender, col = q9_2, pct = pct, n = n)
```

> International research funders and/or foreign researchers dominate the research priorities of my country

```{r}
#| fig-width: 8
#| fig-height: 4
#| out-width: "100%"
df_plot <- compute_pct_by_country(data = df, country = gender, col = q9_3)

plot_pct_by_country(data = df_plot, country = gender, col = q9_3, pct = pct, n = n)
```

> I am satisfied with the way research performance is assessed my organization e.g., academic publications, or obtaining a research grant

```{r}
#| fig-width: 8
#| fig-height: 4
#| out-width: "100%"
df_plot <- compute_pct_by_country(data = df, country = gender, col = q9_4)

plot_pct_by_country(data = df_plot, country = gender, col = q9_4, pct = pct, n = n)
```

> At my organization, there is collaboration rather than competition between researchers

```{r}
#| fig-width: 8
#| fig-height: 4
#| out-width: "100%"
df_plot <- compute_pct_by_country(data = df, country = gender, col = q9_5)

plot_pct_by_country(data = df_plot, country = gender, col = q9_5, pct = pct, n = n)
```

> Do you think career progression (for instance, to senior positions) is harder for certain groups of researchers, e.g., women, early career researchers?

```{r}
#| fig-width: 8
#| fig-height: 4
#| out-width: "100%"
df_plot <- compute_pct_by_country(data = df, country = gender, col = q10)

plot_pct_by_country(data = df_plot, country = gender, col = q10, pct = pct, n = n)
```

```{r}
#| fig-width: 8
#| fig-height: 4
#| out-width: "100%"
df_long <- df |> 
  # Step 1: Split comma-separated q11 into multiple rows
  separate_rows(q11, sep = ",") |> 
  # Step 2: Trim any extra whitespace
  mutate(q11 = str_trim(q11)) |> 
  drop_na(q11)

df_plot <- compute_pct_by_country(data = df_long, country = gender, col = q11)

plot_pct_by_country(data = df_plot, country = gender, col = q11, pct = pct, n = n)
```

## Main questions by career stage

I grouped:

- "Student (BSc, BA, MSc, MA, MPH, MD, PhD)", "Research assistant", "Research fellow, post-doctoral fellow, or other research positions", "Assistant Professor" as "Early-career"
- "Associate Professor", "Full Professor", "Dean or Head of Department" as "Senior"
- The rest ("Lab technician", "Research administrator or manager", "Research doctor or nurse", "Lecturer (main job is teaching, no research)", "Other, please specify:") as "Support staff"

```{r}
df <- df |> 
  mutate(
    career_stage = case_when(
      q7 %in% c("Student (BSc, BA, MSc, MA, MPH, MD, PhD)", "Research assistant", "Research fellow, post-doctoral fellow, or other research positions", "Assistant Professor") ~ "Early-career",
      q7 %in% c("Associate Professor", "Full Professor", "Dean or Head of Department") ~ "Senior",
      q7 %in% c("Lab technician", "Research administrator or manager", "Research doctor or nurse", "Lecturer (main job is teaching, no research)", "Other, please specify:") ~ "Support staff",
    )
  )
```

```{r}
#| fig-width: 3
#| fig-height: 1.5
df_plot <- df |> 
  group_by(career_stage) |>
  count() |> 
  mutate(pct = 100 * n / nrow(df))

ggplot(df_plot, aes(x = fct_rev(career_stage), y = pct)) +
    geom_bar(stat = "identity") +
    geom_text(aes(label = paste0(n, " (", round(pct, 0), "%)")), hjust = -0.1, size = 3) +
    scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
    coord_flip() +
    labs(x = NULL, y = "Percentage") +
    theme_light()
```

By country

```{r}
#| fig-width: 8
#| fig-height: 4
#| out-width: "100%"
df_plot <- compute_pct_by_country(data = df, country = q2, col = career_stage)

plot_pct_by_country(data = df_plot, country = q2, col = career_stage, pct = pct, n = n)
```


> I think research culture is evolving for the better

```{r}
#| fig-width: 8
#| fig-height: 4
#| out-width: "100%"
df_plot <- compute_pct_by_country(data = df, country = career_stage, col = q9_1)

plot_pct_by_country(data = df_plot, country = career_stage, col = q9_1, pct = pct, n = n)
```

> There is equity in decision-making and giving credit for research within my organisation

```{r}
#| fig-width: 8
#| fig-height: 4
#| out-width: "100%"
df_plot <- compute_pct_by_country(data = df, country = career_stage, col = q9_2)

plot_pct_by_country(data = df_plot, country = career_stage, col = q9_2, pct = pct, n = n)
```

> International research funders and/or foreign researchers dominate the research priorities of my country

```{r}
#| fig-width: 8
#| fig-height: 4
#| out-width: "100%"
df_plot <- compute_pct_by_country(data = df, country = career_stage, col = q9_3)

plot_pct_by_country(data = df_plot, country = career_stage, col = q9_3, pct = pct, n = n)
```

> I am satisfied with the way research performance is assessed my organization e.g., academic publications, or obtaining a research grant

```{r}
#| fig-width: 8
#| fig-height: 4
#| out-width: "100%"
df_plot <- compute_pct_by_country(data = df, country = career_stage, col = q9_4)

plot_pct_by_country(data = df_plot, country = career_stage, col = q9_4, pct = pct, n = n)
```

> At my organization, there is collaboration rather than competition between researchers

```{r}
#| fig-width: 8
#| fig-height: 4
#| out-width: "100%"
df_plot <- compute_pct_by_country(data = df, country = career_stage, col = q9_5)

plot_pct_by_country(data = df_plot, country = career_stage, col = q9_5, pct = pct, n = n)
```

> Do you think career progression (for instance, to senior positions) is harder for certain groups of researchers, e.g., women, early career researchers?

```{r}
#| fig-width: 8
#| fig-height: 4
#| out-width: "100%"
df_plot <- compute_pct_by_country(data = df, country = career_stage, col = q10)

plot_pct_by_country(data = df_plot, country = career_stage, col = q10, pct = pct, n = n)
```

```{r}
#| fig-width: 8
#| fig-height: 4
#| out-width: "100%"
df_long <- df |> 
  # Step 1: Split comma-separated q11 into multiple rows
  separate_rows(q11, sep = ",") |> 
  # Step 2: Trim any extra whitespace
  mutate(q11 = str_trim(q11)) |> 
  drop_na(q11)

df_plot <- compute_pct_by_country(data = df_long, country = career_stage, col = q11)

plot_pct_by_country(data = df_plot, country = career_stage, col = q11, pct = pct, n = n)
```